---
title: "APRM: Revising R"
output: 
  learnr::tutorial:
    progressive: true
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(psych)
library(tidyverse)

knitr::opts_chunk$set(echo = FALSE)

data("Tal.Or") 


```


## Overview

In these exercises, we will work with the dataset from Tal-Or et al. (2010) which is preloaded and named *Tal.Or* 

Tal-Or et al. (2010) examined the presumed effect of the media in two experimental studies. These data are from study 2. 

**Abstract:** According to the influence of presumed media influence hypothesis, people estimate the potential effects of media on other people and change their attitudes or behaviors as a consequence. In recent years, many studies offered some support for this idea. However, a central limitation of these studies is that all of them utilized correlational methodology and thus do not offer a valid way to infer causality. The current research examined the causal direction in the influence of presumed media influence using experimental methodology. In Study 2,perceptions regarding the influence of a news story about an expected shortage in sugar were manipulated indirectly, by manipulating the perceived exposure to the news story,and behavioral intentions resulting from the story were consequently measured.

**Experimental hypothesis:**  Participants will be more likely to react to the sugar shortage report when they are manipulated to think that others are more affected by the report.

**Procedure:** Experimenters explained that participants were to answer a short survey about media impact on purchase decisions and handed out randomly two versions of a two page pamphlet. In the first page, participants were asked to read a newspaper article about an expected shortage in sugar that is about to be published in the coming days. In the second page, the participants were asked to answer three questionnaires, one measuring reactions to the publication of the shortage in sugar story, the second served as a manipulation check, and the final set of questions were demographic. After respondents completed the questionnaires, they were debriefed as to the true object of the study and about the fact that the information they received about shortage in sugar was false.

The results are data frame with 123 observations on the following 6 variables:

- **cond**: Experimental Condition: 0 low media importance, 1 high media importance. (Importance was manipulated by telling participants that the story would be published either on the front page of a newspaper or inside the economic suppliment of the newspaper).

- **pmi**: Presumed media influence (This was a manipulation check to see that participants felt that publishing the article would affect people's behaviour and that responses were not different based on age or gender of participants. The value is the mean score of response to two questions.)

- **import**: Importance of the issue (Similar to the pmi variables, a check was also done to see that participants agreed that the issue is important and that responses were not different based on age or gender of participants. "The article is about an important topic concerning the global economic crisis” and “the decision to publish the article on the front/back page is an indication of the topic’s importance”.)

- **reaction**: Subjects rated agreement about possible reactions to the story. (The score is the mean of 4 items: “publishing the article might affect my decisions about buying sugar, “I will buy sugar next time I go to the store,” “I will buy more sugar than usual next time I
go to the store,” and “I will try to reduce my sugar consumption.”).

- **gender**: 1 = male, 2 = female

- **age**: a numeric vector

## Working with data

The following packages have been preloaded into this exercise:
  - psych
  - tidyverse (includes dplyr, ggplot etc.)

The dataset is called **Tal.Or**


### Looking at the dataset

Type the name of the dataset and press *Run Code* to view the data:

```{r data1, exercise=TRUE}

```

### Looking at the first few rows of the dataset 

The *head()* function lets us view a few rows of the dataset to check it. Modify the following code to view the first few rows:

```{r data2, exercise=TRUE, exercise.eval=TRUE}
Tal.Or
```

```{r data2-hint}
head(Tal.Or)
```

### Accessing specific columns/variables of the dataset

Write the code to show only the data from the **pmi** column:

*Hint: Use the dollar sign*

```{r data3, exercise=TRUE}

```

Write the code to show only the first five data values from the pmi column:

```{r data4, exercise=TRUE}

```


### Arranging data

Arrange the data so it is displayed in order of **age** (from lowest to highest):

*Hint: Look in your worksheets (Importing and working with data) for the arrange function*

```{r data5, exercise=TRUE}

```

Arrange the data so it is displayed in order of importance (**import**) (from highest to lowest):

*Hint: Look in your worksheets (Importing and working with data) for the arrange function*

```{r data6, exercise=TRUE}

```

### Filtering data

Filter the dataset to show only males:

*Hint: Look in your worksheets (Importing and working with data) for the filter function*

```{r data7, exercise=TRUE}

```

Filter the dataset to show only females who had a **reaction** greater than 3:

*Hint: Look in your worksheets (Importing and working with data) for the filter function*

```{r data8, exercise=TRUE}

```

### Grouping and summarising data

Summarise the data by condition (**cond**) to show the mean and standard deviation of **reaction**: 

*Hint: Look in your worksheets (Importing and working with data) for the group_by and summarise functions*

```{r data9, exercise=TRUE}

```

### Creating new variables

Use the mutate function to create a new variable called **ageGroup** that categorises people under 30 as *young* and over 30 as *old*:

```{r data10, exercise=TRUE}

```

## Descriptive Statistics

Use the below space to run whatever code is necessary to answer the questions that follow:

```{r desc, exercise=TRUE, exercise.lines = 5 }

```

```{r desc1, echo = FALSE}
question_text(
  "What is the mean reaction score for males?",
  answer("3.45", correct = TRUE),
  allow_retry = TRUE
)
```

```{r desc2, echo = FALSE}
question_text(
  "What is the standard deviation reaction score for males?",
  answer("1.62", correct = TRUE),
  allow_retry = TRUE
)
```
```{r desc3, echo = FALSE}
question_text(
  "What is the mean reaction score for females?",
  answer("3.5", correct = TRUE),
  allow_retry = TRUE
)
```

```{r desc4, echo = FALSE}
question_text(
  "What is the standard deviation reaction score for females?",
  answer("1.52", correct = TRUE),
  allow_retry = TRUE
)
```

```{r desc5, echo = FALSE}
question_radio(
  "Using visual checks and then statistical tests, are the reaction data normally distributed?",
  answer("no", correct = TRUE),
  answer("yes", message = 'Check Shapiro Wilks.'),
  allow_retry = TRUE
)
```

Use the **describeBy** function to summarise all descriptive stats by condition (**cond**):
```{r desc6, exercise=TRUE}

```

```{r desc7, echo = FALSE}
question_radio(
  "Which condition has more participants?",
  answer("Low importance", correct = TRUE),
  answer("High Importance"),
  allow_retry = TRUE
)
```

## Graphs and data visualisation

Using ggplot, we will create some graphs to summarise the data from the study. This will require combining some code examples from previous sections. 

### Creating a scatterplot with ggplot

The code below will only create a blank plot because it is missing the *geom* to display the data. Geoms are the the "shapes" that we use to display our data and can be points, bars, histograms, boxplots etc.

Modify the code below by adding the correct geom (geom_point) to complete the scatterplot:

*Check your "Graphs and Data Visualisation in R" worksheet for guidance*

```{r gg1, exercise=TRUE, eval=TRUE}

ggplot(data = Tal.Or, aes(x = age, y = reaction))


```

Once your scatterplot is displaying correctly, modify the code again so that the colour of the points is based on the **cond** variable. 

### Creating a histogram with ggplot

Use ggplot to create a histogram of **reaction** 

*Hint: Histograms have their data on the x axis and nothing on the y axis*

```{r gg2, exercise=TRUE}

```

### Creating a bar chart with summary data (e.g. mean) in ggplot

```{r gg3, exercise = TRUE}

```

```{r gg3-hint}
ggplot(data=Tal.Or, aes(x=cond, y= reaction, fill=cond)) +
stat_summary(fun.y = "mean", geom = "bar")
```

**Question: What's up with the bar chart colours and how can we fix this?"**

## Correlation

We want to check if there is any relationship between **age** and perceived media importance (**pmi**). Generatre a scatterplot and then run a correlation analysis to answer this question: 

```{r cor1, exercise=TRUE}

```

```{r cor1-hint}
plot(Tal.Or$age, Tal.Or$pmi)
cor.test()

```

```{r cor2, echo = FALSE}
question_radio(
  "Is there a significant correlation between pmi and age?",
  answer("Yes", correct = TRUE),
  answer("No"),
  allow_retry = TRUE
)
```

There seems to be a few outliers over the age of 30 that could be influencing the previous result. Using the filter command, create a subset of the data that only includes participants over 30 and run the correlation analysis again:

```{r cor3, exercise=TRUE}

```

```{r cor3-hint}
mySubset <- Tal.Or %>% filter()

cor.test(mySubset$age, mySubset$pmi)

```


```{r cor4, echo = FALSE}
question_radio(
  "Is there a significant correlation between pmi and age when outliers are removed?",
  answer("Yes"),
  answer("No", correct = TRUE),
  allow_retry = TRUE
)
```

**Note: we will use the full data set for all analyses during this exercise.**

Run a similar analysis to the above, to check whether there is any correlation between importance (**import**) and **age**:

```{r cor5, exercise=TRUE}

```

## Tests of difference:

Check the mean scores of **reaction** in each condition (**cond**) to see if participants in the “high importance” condition scored higher on the behavioral reaction scale compared to participants in the “low importance” condition:


```{r tod1, exercise=TRUE}

```

Use a t-test to test the hypothesis that participants in the “high importance” condition scored higher on the behavioral reaction scale compared to participants in the “low importance” condition (i.e. is there a significant difference?):

```{r tod2, exercise=TRUE}

```

```{r tod2-hint, exercise=TRUE}
#format for t-test:
t.test(dv ~ iv)
```

```{r tod3, echo = FALSE}
question_radio(
  "Is there a significant difference in reaction between conditions?",
  answer("Yes"),
  answer("No", correct = TRUE),
  allow_retry = TRUE
)
```

## Regression

We want to check which factors significantly predicted **reaction**. Condition (**cond**) is our main predictor, as this is the variable that was manipulated during the experiment. However, there are also demographic variables (**age** and **gender**) as well as the two variables that the researchers anticipated could affect the reaction: Presumed media influence (**pmi**) and Importance of the issue (**import**).

Based on this understanding of the variables, it seems logical to think about the predictors in "blocks" and add them sequentially to a heirarchical regression. To do this, we will first run an analysis that only includes the intercept (model0), then the condition (**cond**) variable (model1), then add **pmi** and **import** (model2), finally adding demographics (**age** and **gender**).

Looking at the output at each step of the way, we can decide on a final model which only includes variables that significantly predict variance in the outcome (i.e. reaction). We want to be sure to check the assumptions of the model to ensure reliability and accuracy of predictions.

### Model 0 (just the intercept)

To give us a baseline for comparison, we need to run an analysis with just the intercept:

*Remember: The lm function is used to run regression. We need to save that result to a variable (model0) and use the summary function to view the result.*  

```{r reg1, exercise=TRUE}

```

```{r reg1-hint}
model0 <- lm(Tal.Or$reaction ~ 1)

```

### Model 1 (condition)

Run a regression analysis to see if condition (**cond**) significantly predicts **reaction**:

```{r reg2, exercise=TRUE}

```


### Model 2 (condition + importance + presumed media influence)

*Note: use a plus sign (+) in your code to seperate predictor variables*

Add the variables **pmi** and **import** and ...

- Assess the model overall
- Identify which individual variables are significant
- Examine which variables are more important in predicting reaction 

```{r reg3, exercise=TRUE}

```

```{r reg4, echo = FALSE}
question_radio(
  "Is the overall model significant (model 2)?",
  answer("Yes", correct = TRUE),
  answer("No"),
  allow_retry = TRUE
)
```

```{r reg5, echo = FALSE}
question_radio(
  "Which preictor has the strongest relationship with the variance in reaction (model 2)?",
  answer("cond", message = "Look at the coefficients table"),
  answer("pmi", correct = TRUE),
  answer("import", message = "Look at the coefficients table"),
  allow_retry = TRUE
)
```

### Model 3 (condition + importance + presumed media influence + age + gender)

This model includes all of the predictor variables that we have. 

- Assess the model overall
- Identify which individual variables are significant
- Examine which variables are more important in predicting reaction 

```{r reg6, exercise=TRUE}

```

### Model 4 (condition and whichever other variables were significant)

For this model, use the **cond** variable as a predictor and also include any other variables that were significant in your previous models. 

```{r reg7, exercise=TRUE}

```

Use the plot function to check the assumptions of regression on Model 4 and answer the questions that follow:

```{r reg8, exercise=TRUE}

```

### Model 5 (Model 4 but with interactions) 

This time we will use the same predictors as Model 4, but seperate them using an asterisk (*) instead of a plus sign. This will allow us to test for any interactions between variables. 

```{r reg9, exercise=TRUE}

```

